3D-printable micropipette (Figures and Tables)

### 2015-01-26 publishing/plos_template.tex
spell checke

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}

@@

3D printing as a form of additive manufacturing has existed for decades althought the recent avalibilty of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.

The open source software movement and has spawned the additional areas of open source hardware, such as microcontroller boards (Arduino) as well as 3D printers themselves (RepRap).
Open source scientific instruments and laboratory equipment are being actively developed(openpcr.org, opensource lab book.)
3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material. 
In addition, end users can customize the equiment to their application. 
Some of the more clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device.
For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some finacial barriers of entry.

Printable micropipette designs can be found on 3D-part sharing websites (thiniverse).
While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes nor have any been rigorously validated.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.

@@

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Design}
The device is designed to actuate a pipette to a set distance.
The pipette is plunger is actuated to three points, two fixed and one adjustable.
The fixed points are the dispensed point, when the plunger is all the way down, and the reset point, when the plunger is ready to withdraw fluid.
The adjustable point is the set point, which determines the volume of fluid that will be drawn into the pipette and dependes on the position of the screw.
The system is spring loaded towards the set point.
A springed notch, in the plunger shaft part, and a groove, in the body part, hold the plunger at the reset position where it can be released by pressing in the notch.
A 1 mL BD syringe twists to lock into the body part.
An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.

@@

3D parts were designed in Blender and SolidWorks and printed by Fineline Protoypeing via selective laser sintering. 
Additional materials include a spring, a nut and bolt and two washers.

@@

The pipette was validated and compared to a commerical pipette. 
The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
To test the pipette the same volume was pipetted 50 times without moveing or re-adjusting the set point. 
The printed pipette's accuracy and precicion was charaterized and compared to a commericial pipette.

% Results and Discussion can be combined.
\section*{Results}

% We only support three levels of headings, please do not create a heading level below \subsubsection.
\subsection*{Subsection 1}

@@

\begin{table}[!ht]
\caption{
\bf{Comparision of Accuracy and Precision}}
\begin{tabular}{|c|c|c|c|}
\hline
    Target Volume & 20 $\mu$L & 50 $\mu$L & 200 $\mu$L  \\
    \hline
    Printed Pipette & 196.4 $\pm$ 2.2 & 53.5 $\pm$ 1.8 & 19.5 $\pm$ 0.6 \\
    Commercial Pipette & 204.5 $\pm$ 2.9 & 49.9 $\pm$ 0.1 & 19.9 $\pm$ 0.2 \\
    \hline
\end{tabular}
\begin{flushleft} Average measured volume by weight and standard deviation.
\end{flushleft}
\label{tab:comp}
 \end{table}

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author Summary}

@@

3D printing as a form of additive manufacturing has existed for decades although the recent availability of inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.

The open source software movement and has spawned the additional areas of open source hardware, such as micro controller boards (Arduino) as well as 3D printers themselves (RepRap).
Open source scientific instruments and laboratory equipment are being actively developed(openpcr.org, opensource lab book.)
3D-printable lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the raw material. 
In addition, end users can customize the equipment to their application. 
Some of the more clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device.
For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges and could allow researchers in the developing world to better participate in science by reducing some financial barriers of entry.

Printable micropipette designs can be found on 3D-part sharing websites (thingiverse).
While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes nor have any been rigorously validated.
We present a pipette constructed from 3D printed parts that allows a 1 ml syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.

@@

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Design}
The device is designed to actuate a pipette to a set distance.
The pipette is plunger is actuated to three points, two fixed and one adjustable.
The fixed points are the dispensed point, when the plunger is all the way down, and the reset point, when the plunger is ready to withdraw fluid.
The adjustable point is the set point, which determines the volume of fluid that will be drawn into the pipette and depends on the position of the screw.
The system is spring loaded towards the set point.
A spring notch, in the plunger shaft part, and a groove, in the body part, hold the plunger at the reset position where it can be released by pressing in the notch.
A 1 ml BD syringe twists to lock into the body part.
An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.

@@

3D parts were designed in Blender and SolidWorks and printed by Fineline Prototyping via selective laser sintering. 
Additional materials include a spring, a nut and bolt and two washers.

@@

The pipette was validated and compared to a commercial pipette. 
The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
To test the pipette the same volume was pipetted 50 times without moving or re-adjusting the set point. 
The printed pipette's accuracy and precision was characterized and compared to a commercial pipette.
The printed pipette and a series of commercial pipettes were tested at volumes of 20 $\mu$L 50 $\mu$L and 200 $\mu$L.
The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for variability
Measurements were taken from the commercial pipette in a similar way.

To test user friendliness and feasibility for using the pipette without verifying with a scale, data was also gathered from novice users.
After a quick overview of the operation of the pipette measurements were taken after the volunteers adjusted the pipette to 200, 50, 20 and 10 $\mu$L.
After the first attempt was measured on the scale the volunteer was allow to adjust the set point and re-measure until within 15\% of the target volume was reached.

% Results and Discussion can be combined.
\section*{Results and Discussion}

Our printed pipette had a comparable accuracy to a commercial pipette (table 1).
The commercial pipette has a digital readout that allows the user to adjust precisely to set values where the printed pipette is adjusted by eye according to graduations.
This is certainly the cause of the lower accuracy and wider deviation although it's performance is impressive.

The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurements without validating with a scale (Figure3).
% We only support three levels of headings, please do not create a heading level below \subsubsection.
\subsection*{Subsection 1}

@@

\begin{table}[!ht]
\caption{
\bf{Comparison of Accuracy and Precision}}
\begin{tabular}{|c|c|c|c|}
\hline
    Target Volume & 20 $\mu$L & 50 $\mu$L & 200 $\mu$L  \\
    \hline
    Printed Pipette & 196.4 $\pm$ 2.2 & 53.5 $\pm$ 1.8 & 19.5 $\pm$ 0.6 \\
    Commercial Pipette & 204.5 $\pm$ 2.9 & 49.9 $\pm$ 0.1 & 19.9 $\pm$ 0.2 \\
    \hline
\end{tabular}
\begin{flushleft} Average measured volume by weight and standard deviation.
\end{flushleft}
\label{tab:comp}
 \end{table}
